Data preparation for team category analysis

### 2023-05-17 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Adding notes for the aggregate whole period variables.

### Employee, whole period variables

For following variables are aggregated for the whole period for each employee:

-   Proportion of days onsite

-   Proportion of days remote

-   Number of working days

@@

$OnsiteDays_m$ is the number of onsite days for team member $m$ and $TeleworkDays_m$ is the number of telework days for team member $m$. $x$ is number of members on team

@@

@@

@@

@@

@@

@@

@@

@@

For following variables are aggregated for the whole period by day of the week for each employee:

-   Proportion of days remote by the day of the week

-   Correlation of work status between days of the week

>>>>

### Team, whole period variables

For following variables are aggregated for the whole period for the whole team:

-   Proportion of team members working days onsite

-   Proportion of team members working days remote

-   Number of team members working days

@@

$OnsiteDays_m$ is the number of onsite days for team member $m$ and $TeleworkDays_m$ is the number of telework days for team member $m$. $x$ is number of members on team.

@@

Now we calculate the values for the data.

First count the number of distinct days per `supervisor_e_mail_address`, `person_id`, and `daily_status_imputed`, then filter to daily status: *Reporting to Job Site* or *Teleworking*.

@@

Second, sum the number days by `supervisor_e_mail_address` from dataframe `prep_a`.

@@

Third, sum the number days by `supervisor_e_mail_address` and `daily_status_imputed` from dataframe `prep_a` and reshape the data wide so that statuses are in columns, `daily_status_*`.

@@

Fourth, count the number of unique team members per supervisor.

@@

Join working days, working days per status, and team members into one datafram by `supervisor_e_mail_address`.

@@

Calucate `observation_window_days`, `daily_status_reporting_to_job_site_working_prop`, `daily_status_teleworking_working_prop`, `daily_status_reporting_to_job_site_observation_prop`, and `daily_status_teleworking_observation_prop`, then replace missing values with zero.

@@

-   Modal size of team over observation window

-   Proportion of team members working days remote by the day of the
    week

-   Proportion of team members exiting team

-   Proportion of working days at least two team member co-located

-   Proportion of working days supervisor is co-located with at least
    one team member

-   Proportion of working days entire team is co-located

-   Proportion of working days entire team is remote

-   Proportion of observation window the team existed.

@@

For following variables are aggregated for the whole period by day of the week for the whole team:

-   Proportion of team members working days remote by the day of the
    week
